The Deviation of China Map as a Regression Problem

### 2012-12-07 paper.tex
meh

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}

@@

Figure~\ref{fig:fxy-degree}(right) shows the plot where the deviation is
measured in meters.
It's a linear function, thus we can do a simple linear regression.
\begin{verbatim}
> dx=dx.*cos(y./180.*pi).*6371000.*pi./180;
> mx=[ones(size(y)),y]; std(mx*(pinv(mx)*dx)-dx)
ans =  0.14664
> pinv(mx)*dx
ans =
   406.3954
     2.5241
\end{verbatim}
The standard error, 0.14664 meter, is acceptable, because the input data's
resolution is about 0.6 meter\footnote{The input is converted from google map's
unit. One unit is one pixel under the maximum zoom setting. Due to Mercator
projection, higher latitude has higher resolution. The average 0.6 meter is
computed based on the mean coordinate, which is near Xi'an city.} on average.
The final function is
\begin{equation}
f_x(110.16,y)=406.3954+2.5241y
\end{equation}
After trying out other constant longitudes,
we find out that the two coefficients are different for different longitude.
We have
\begin{equation}
f_x(x,y)=g_1(x)+g_2(x)\times y
\label{eq:fxy}
\end{equation}
where $g_1(x)$ and $g_2(x)$ are not yet known.

@@

\begin{verbatim}
> atan(0.82075/13.30099)
ans =  0.061628
> atan(0.27150/13.33287)
ans =  0.020360
> mx=[ones(size(x)),x,sin(2.*pi.*x-0.020360),sin(6.*pi.*x-0.061628)];
> std(mx*(pinv(mx)*dy)-dy)
ans =  0.38114
> pinv(mx)*dy
ans =
  -160.4519
     2.4276
    13.3356
    13.3263
\end{verbatim}
So the function is
\begin{eqnarray}
f_y(x,39.36) & = & -160.45195+2.42764x+13.33287sin(2\pi x) \nonumber \\
             &   & -0.27150cos(2\pi x)+13.30099cos(6\pi x)-0.82075cos(6\pi x) \nonumber \\
             & = & -160.45195+2.42764x+13.3356sin(2\pi x-0.061628) \nonumber \\
             &   & +13.3263cos(6\pi x-0.020360)
\end{eqnarray}

After trying out other constant latitudes, we find out that the first two
coefficients to be changing but the last 4 coefficients to be fixed.
Thus, we know
\begin{eqnarray}
f_y(x,y) & = & g_1(y)+g_2(y)x+13.3356sin(2\pi x-0.061628) \nonumber \\
         &   & +13.3263cos(6\pi x-0.020360)
\end{eqnarray}
where $g_1(y)$ and $g_2(y)$ are not yet known.

@@

Now let's merge sin and cos.
\begin{verbatim}
> atan(2.0044e+02/8.3824e-01)
ans =  1.5666
> atan(7.0449e+01/7.0435e+01)
ans =  0.78550
> atan(9.1218e-02/2.6699e+01)
ans =  0.0034165
> atan(1.3044e-01/1.3342e+01)
ans =  0.0097763
> atan(2.7504e-01/1.3342e+01)
ans =  0.020612
> atan(8.2298e-01/1.3306e+01)
ans =  0.061772
> mx=[ones(size(x)),x,x.*x,sin(pi.*x./30+1.5666),sin(pi.*x./12+0.78550),\
  sin(pi.*x./3-0.0034165),sin(pi.*x-0.0097763),sin(2.*pi.*x-0.020612),\
  sin(6.*pi.*x-0.061772)]; std(mx*(pinv(mx)*dx)-dx)
ans =  0.38668
> pinv(mx)*dx
ans =
   1.2051e+03
  -1.8402e+01
   9.4012e-02
   2.0045e+02
  -9.9620e+01
  -2.6699e+01
  -1.3343e+01
   1.3344e+01
   1.3332e+01
\end{verbatim}

@@

After trying out other constant latitude, we found that only the first two
coefficients are affected by latitude. The rest of the coefficients do not
change. Thus, we have
\begin{eqnarray}
f_x(x,y) &=& g_1(y) -g_2(y)x +0.094012x^2 +200.45sin(\pi x/30+1.5666) \nonumber \\
         & & -99.62sin(\pi x/12+0.78550) -26.699sin(\pi x/3-0.0034165) \nonumber \\
         & & -13.343sin(\pi x-0.0097763) +13.344sin(2\pi x-0.020612) \nonumber \\
         & & +13.332sin(6\pi x-0.061772)
\end{eqnarray}
where $g_1(y)$ and $g_2(y)$ are not yet known.

@@

We have
\begin{eqnarray}
f_y(110.16,y) &=& 162.09-22.422y+0.41568y^2 \nonumber \\
              & & -181.69sin(\pi y/30-0.31442)-108.99sin(\pi y/12+0.27267) \nonumber \\
              & & +26.643sin(\pi y/3+1.05)-13.357sin(\pi y-0.00459) \\
f_y(x,y)      &=& g_1(x)+g_2(x)y+0.41568y^2 \nonumber \\
              & & -181.69sin(\pi y/30-0.31442)-108.99sin(\pi y/12+0.27267) \nonumber \\
              & & +26.643sin(\pi y/3+1.05)-13.357sin(\pi y-0.00459)
\end{eqnarray}

@@

From Equation~\ref{eq:fxx} and \ref{eq:fxy} we know that $f_x(x,y)$ and
$f_y(x,y)$ must be in the following form.

\begin{eqnarray}
f_x(x,y) &=& a_1+a_2x+a_3y+a_4xy+a_5x^2 \nonumber \\
         & & +a_6sin(\pi x/30+b_1) +a_7sin(\pi x/12+b_2)+a_8sin(\pi x/3+b_3) \nonumber \\
         & & +a_9sin(\pi x+b_4)+a_{10}sin(2\pi x +b_5) +a_{11}sin(6\pi x+b_6) \\
f_y(x,y) &=& c_1 +c_2x +c_3y +c_4xy +c_5y^2 \nonumber \\
         & & +c_6sin(\pi y/30+d_1)+c_7sin(\pi y/12 +d_2)+c_8sin(\pi y/3+d_3) \nonumber \\
         & & +c_9sin(\pi y+d_4)+c_{10}sin(2\pi x+d_5) +c_{11}sin(6\pi x +d_6)
\end{eqnarray}

Applying the previous method on the data file \url{google-grid40.tsv}, we can
determine all the parameters easily.
The octave commands are skipped.
The resulting equations are shown below and their standard errors are 0.4373
and 0.43998 meters respectively.

@@

To verify their correctness, we can compute the deviated coordinates of Monument
to the People's Heroes using its true coordinates.
$f_x(116.391667,39.903056)=531.91$ meters and
$f_y(116.391667,39.903056)=155.39$ meters.
This means that the deviated coordinate is 531.91 meters to the east and 155.39
to the north, thus $x'=116.391667+531.91\times 360/(2\pi\times 6371000\times
cos(2\pi\times 39.903056/360))=116.397903$ and $y'=39.903056+155.39\times
360/(2\pi\times 6371000)=39.904453$.
We now put the deviated coordinate in a deviated map as in Figure~\ref{fig:map-jjmdd}.
It aligns nicely.

>>>>

%6378137 EARTH_RADIUS in https://developers.google.com/maps/documentation/flash/reference
\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}

@@

Figure~\ref{fig:fxy-degree}(right) shows the plot where the deviation is
measured in meters.
It's a linear function, thus we can do a simple linear regression.
\begin{verbatim}
> dx=dx.*cos(y./180.*pi).*6371000.*pi./180;
> mx=[ones(size(y)),y]; std(mx*(pinv(mx)*dx)-dx)
ans =  0.14664
> pinv(mx)*dx
ans =
   406.3954
     2.5241
\end{verbatim}
The standard error, 0.14664 meter, is acceptable, because the input data's
resolution is about 0.6 meter\footnote{The input is converted from google map's
unit. One unit is one pixel under the maximum zoom setting. Due to Mercator
projection, higher latitude has higher resolution. The average 0.6 meter is
computed based on the mean coordinate, which is near Xi'an city.} on average.
The final function is
\begin{equation}
f_x(110.16,y)=406.3954+2.5241y
\end{equation}
After trying out other constant longitudes,
we find out that the two coefficients are different for different longitude.
We have
\begin{equation}
\label{eq:fxy}
f_x(x,y)=g_1(x)+g_2(x)\times y
\end{equation}
where $g_1(x)$ and $g_2(x)$ are not yet known.

@@

\begin{verbatim}
> atan(-0.82075/13.30099)
ans =  -0.061628
> atan(-0.27150/13.33287)
ans =  -0.020360
> mx=[ones(size(x)),x,sin(2.*pi.*x-0.020360),sin(6.*pi.*x-0.061628)];
> std(mx*(pinv(mx)*dy)-dy)
ans =  0.38114
> pinv(mx)*dy
ans =
  -160.4519
     2.4276
    13.3356
    13.3263
\end{verbatim}
So the function is
\begin{eqnarray}
f_y(x,39.36) & = & -160.45195+2.42764x+13.33287sin(2\pi x) \nonumber \\
             &   & -0.27150cos(2\pi x)+13.30099cos(6\pi x)-0.82075cos(6\pi x) \nonumber \\
             & = & -160.45195+2.42764x+13.3356sin(2\pi x-0.061628) \nonumber \\
             &   & +13.3263cos(6\pi x-0.020360)
\end{eqnarray}

After trying out other constant latitudes, we find out that the first two
coefficients to be changing but the last 4 coefficients to be fixed.
Thus, we know
\begin{eqnarray}
\label{eq:fyx}
f_y(x,y) & = & g_1(y)+g_2(y)x+13.3356sin(2\pi x-0.061628) \nonumber \\
         &   & +13.3263cos(6\pi x-0.020360)
\end{eqnarray}
where $g_1(y)$ and $g_2(y)$ are not yet known.

@@

Now let's merge sin and cos.
\begin{verbatim}
> atan(2.0044e+02/8.3824e-01)
ans =  1.5666
> atan(-7.0449e+01/-7.0435e+01)
ans =  0.78550
> atan(9.1218e-02/-2.6699e+01)
ans =  -0.0034165
> atan(1.3044e-01/-1.3342e+01)
ans =  -0.0097763
> atan(-2.7504e-01/1.3342e+01)
ans =  -0.020612
> atan(-8.2298e-01/1.3306e+01)
ans =  -0.061772
> mx=[ones(size(x)),x,x.*x,sin(pi.*x./30+1.5666),sin(pi.*x./12+0.78550),\
  sin(pi.*x./3-0.0034165),sin(pi.*x-0.0097763),sin(2.*pi.*x-0.020612),\
  sin(6.*pi.*x-0.061772)]; std(mx*(pinv(mx)*dx)-dx)
ans =  0.38668
> pinv(mx)*dx
ans =
   1.2051e+03
  -1.8402e+01
   9.4012e-02
   2.0045e+02
  -9.9620e+01
  -2.6699e+01
  -1.3343e+01
   1.3344e+01
   1.3332e+01
\end{verbatim}

@@

After trying out other constant latitude, we found that only the first two
coefficients are affected by latitude. The rest of the coefficients do not
change. Thus, we have
\begin{eqnarray}
\label{eq:fxx}
f_x(x,y) &=& g_1(y) -g_2(y)x +0.094012x^2 +200.45sin(\pi x/30+1.5666) \nonumber \\
         & & -99.62sin(\pi x/12+0.78550) -26.699sin(\pi x/3-0.0034165) \nonumber \\
         & & -13.343sin(\pi x-0.0097763) +13.344sin(2\pi x-0.020612) \nonumber \\
         & & +13.332sin(6\pi x-0.061772)
\end{eqnarray}
where $g_1(y)$ and $g_2(y)$ are not yet known.

@@

We have
\begin{eqnarray}
f_y(110.16,y) &=& 162.09-22.422y+0.41568y^2 \nonumber \\
              & & -181.69sin(\pi y/30-0.31442)-108.99sin(\pi y/12+0.27267) \nonumber \\
              & & +26.643sin(\pi y/3+1.05)-13.357sin(\pi y-0.00459) \\
\label{eq:fyy}
f_y(x,y)      &=& g_1(x)+g_2(x)y+0.41568y^2 \nonumber \\
              & & -181.69sin(\pi y/30-0.31442)-108.99sin(\pi y/12+0.27267) \nonumber \\
              & & +26.643sin(\pi y/3+1.05)-13.357sin(\pi y-0.00459)
\end{eqnarray}

@@

From Equation~\ref{eq:fxx} and \ref{eq:fxy} we know that $f_x(x,y)$ must be in
the form of Equation~\ref{eq:fxp}.  Similarly, from Equation~\ref{eq:fyx} and
\ref{eq:fyy} we know $f_y(x,y)$ must be in the form of Equation~\ref{eq:fyp}.
What's left now is to determine the parameters.

\begin{eqnarray}
\label{eq:fxp}
f_x(x,y) &=& a_1+a_2x+a_3y+a_4xy+a_5x^2 \nonumber \\
         & & +a_6sin(\pi x/30+b_1) +a_7sin(\pi x/12+b_2)+a_8sin(\pi x/3+b_3) \nonumber \\
         & & +a_9sin(\pi x+b_4)+a_{10}sin(2\pi x +b_5) +a_{11}sin(6\pi x+b_6) \\
\label{eq:fyp}
f_y(x,y) &=& c_1 +c_2x +c_3y +c_4xy +c_5y^2 \nonumber \\
         & & +c_6sin(\pi y/30+d_1)+c_7sin(\pi y/12 +d_2)+c_8sin(\pi y/3+d_3) \nonumber \\
         & & +c_9sin(\pi y+d_4)+c_{10}sin(2\pi x+d_5) +c_{11}sin(6\pi x +d_6)
\end{eqnarray}

Applying the previous linear regression method on the data file
\url{google-grid40.tsv}, we can determine all the parameters easily.
The octave commands are skipped.
The resulting equations are shown below and their standard errors are 0.4373
and 0.43998 meters respectively, which are larger than the
four 1D cases, but still below the input data's resolution.

@@

To check their correctness, we can compute a deviated coordinate and check
whether it aligns with the deviated map.
We now compute the deviated coordinate of the Monument to the People's Heroes
using its true coordinate $(116.391667,39.903056)$.
$f_x(116.391667,39.903056)=531.91$ meters and
$f_y(116.391667,39.903056)=155.39$ meters.
This means that the deviated coordinate is 531.91 meters to the east and 155.39
to the north.
We then convert meters into degrees and adds them to the true coordinate.

\begin{eqnarray}
x' &=& 116.391667+531.91\times 360/(2\pi\times 6371000\times cos({2\pi \over 360}\times 39.903056)) \nonumber \\
   &=& 116.397903 \nonumber \\
y' &=& 39.903056+155.39\times 360/(2\pi\times 6371000) \nonumber \\
   &=& 39.904453 \nonumber
\end{eqnarray}

We now put the deviated coordinate in a deviated map as in
Figure~\ref{fig:map-jjmdd}.  It aligns nicely.
